### 2014-02-05  feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/abstract.tex
Update

Feature selection is important in many practical classification
settings to address computational constraints or to prevent
overfitting when the data may be high-dimensional but contain
relatively few samples.  While a wide variety of feature selection
methods have been proposed in the literature, little research seems to
focus on feature selection specifically targeted for precision or
recall.  In this paper we propose a novel probabilistic model of
feature selection and argue that MAP inference w.r.t. to two extreme
objectives in this model respectively yield high precision and high
recall feature selection.  From each objective, we then derive an
efficient formula for feature selection in the filtering framework
(i.e., greedy forward selection) and we empirically compare the
resulting feature selection criteria to a wide variety of existing
methods.  Results show that our high precision and high recall feature
selection approaches improve their intended objectives and more
reliably than existing methods whose precision and recall performance
may vary widely across datasets and classifiers.

>>>>

Feature selection is important in many practical supervised learning
settings to address computational constraints or to prevent
overfitting when the data may be high-dimensional but contain
relatively few samples.  While a wide variety of feature selection
methods have been proposed in the literature, little research seems to
focus on feature selection specifically targeted to improve recall in
the case of binary classification.  In this paper we propose a novel
probabilistic voting model of feature selection and argue that
choosing features so as to maximize likelihood objectives w.r.t. this
model provides an effective method for high recall feature selection.
For each objective, we derive an efficient formula for feature
selection in the filtering framework (i.e., greedy forward selection)
and we empirically compare the resulting feature selection criteria to
a wide variety of existing methods.  Results show that our high recall
feature selection approach does indeed improve recall with
improvements most significant when there is a high feature to data ratio.
Such results provide a novel and efficient feature selection algorithm
to target high-recall classification tasks.
